Executive Summary
--------------------------------------------------------
We look at estimate an OLS model, regressing mileage on an automatic/manual dummy. Find a significantly negative effect of automatic on mileage. We redo the estimation as TSLS, using weight as an instument for automatic. These results are even more significant.

Analysis
--------------------------------------------------------
We start by loading the **mtcars** data frame and recode **am** to a logical **automatic** variable.

```{r echo=TRUE, eval=TRUE}
data( mtcars )
mtcars$automatic <- mtcars$am == 0
attach( mtcars )
```

We do some exploratory data analysis on the distribution of the automatic variable (Appendix).

We estimate the Ordinary Least Squares (OLS) model.

```{r echo=TRUE, eval=TRUE}
ols <- lm( mpg ~ automatic, data=mtcars )
summary( ols )
```

There is a significant negative effect of automatic on milage.

We redo the estimation using Two-Stage Least Squares (TSLS), using weight (**wt**) as an instrument for automatic.

```{r echo=TRUE, eval=TRUE}
tsls.fs <- lm(automatic ~ wt)
tsls <- lm(mpg ~ tsls.fs$fitted.values)
summary(tsls)
```

This coefficient is even more negative, and even more significant. We finally plot the residuals for both estimations (Appendix).

The residuals of the OLS estimation appear to be normally distibuted, the TSLS somewhat less, though **n** is too small to make any real claims.

Appendix: Figures
--------------------------------------------------------
```{r echo=TRUE, eval=TRUE, fig.width=10, fig.height=3}
par( mfrow=c(1,2) )
hist( mpg[which(automatic == TRUE)] )
hist( mpg[which(automatic == FALSE)] )
```

We plot the residuals of the OLS and TSLS estimations.

```{r echo=TRUE, eval=TRUE, fig.width=10, fig.height=3}
par( mfrow=c(1,3) )
hist( ols$residuals )
hist(tsls.fs$residuals)
hist( tsls$residuals )
```